Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-06 Paper.tex
trivial changes only - typos and obvious grammar correction - consistent standard orthography: block-chain, block chain -> blockchain, back-end -> backend - minor reorg - . deleted for multiplication in equations - a few convoluted sentences simplified

\begin{abstract}
The block-chain paradigm when coupled with cryptographically-secured transactions has demonstrated its utility through a number of projects, not least Bitcoin. Each such project can be seen as a simple application on a decentralised, but singleton, compute resource. We can call this paradigm a transactional singleton machine with shared-state.

@@

and $f$ is the Ethereum state transition function. In Ethereum, $f$, together with $S$ are considerably more powerful then any existing comparable system; $f$ allows components to carry out arbitrary computation to be done, while $S$ allows components to store arbitrary state between transactions.

@@

This is the basis of the block-chain paradigm, a model that forms the backbone of Ethereum.

@@

Since the system is decentralised and all parties have an opportunity to create a new block on some older pre-existing block the resultant structure is necessarily a tree of blocks. In order to form a consensus as to which path, from root (the genesis block) to leaf (the block containing the most recent transactions) through this tree structure, known as the block-chain, there must be an agreed-upon scheme. If there is ever a disagreement between nodes as to which root-to-leaf path down the block-tree is the `best' block-chain, then a \textit{fork} occurs.

This would mean that past a given point in time (block), there is a temporal co-existance of multiple states of the system: some nodes believing one block to contain the canonical transactions, other nodes believing some other block to be canonical, potentially containing radically different or incompatible transactions. This is to be avoided at all costs as the uncertainty that would ensue would likely kill all confidence in the entire system.

@@

The world-state (\textit{state}, see Appendix \ref{app:state}), is a mapping between addresses (160-bit identifiers) and account states (a data structure serialised as RLP). Though not stored on the block chain, it is assumed that the implementation will maintain this mapping in a modified Merkle Patricia tree (\textit{trie}, see Appendix \ref{app:trie}). The trie requires a simple database back-end that maintains a mapping of bytearrays to bytearrays; we name this underlaying database the state database. This has a number of benefits; firstly the root node of this structure is cryptographically dependent on all internal data and as such its hash can be used as a secure identity for the entire system state. Secondly, being an immutable data structure, it allows any previous state (whose root hash is known) to be recalled by simply altering the root hash accordingly. Since we store all such root hashes in the block chain, we are able to trivially revert to old states.

@@

A transaction is a single cryptographically signed instruction sent by an actor external to Ethereum. e.g. This might be from a person (via a mobile device or desktop computer) or could be from a piece of automated software running on a server. There are two types of transactions: those which result in message calls and those which result in the creation of new contracts. Both types specify a number of common fields:

@@

Both \textbf{body} and \textbf{init} are EVM-code fragments; \textbf{body} is executed each time the contract account receives a message call (either through a transaction or due to the internal execution of code). \textbf{init} is a piece of code executed only once and at contract creation. It gets discarded immediately.

@@

This mechanism enforces a homeostasis in terms of the time between blocks; a smaller period between the last two blocks results in an increase in the difficulty level and thus additional computation required, lengthening the likely next period. Conversely, is the period is too large the difficulty, and expected time to the next block, is reduced.

@@

Where $\mathcal{P}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, then the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

The other two components in the block are simply a list of the transactions (as defined previously) and a list of uncle headers (of the same format as above).

@@

Any ether used to purchase gas that is not refunded is delivered to the \textit{coinbase} address, the address of an account typically under control of the miner. Transactors are free to specify any \textbf{gasPrice} that they wish, however miners are free to ignore transactions as they choose. A higher gas price on a transaction will therefore cost the sender more in terms of Ether and deliver a greater value to the miner and thus will more likely be selected for inclusion by more miners. Miners, in general, will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.

@@

\begin{enumerate}
\item The transaction signature is valid;
\item the transaction nonce is valid (equivalent to the sender account's current nonce);
\item the gas limit is no smaller that the intrinsic gas, $g_i$, used by the transaction;
\item the sender account balance contains at least the cost, $c$, (in wei) required in up-front payment;
\end{enumerate}

where:

\begin{eqnarray}
g_i & \equiv & \begin{cases}
  |\mathbf{d}|.G_{data} + G_{call} & \quad \text{call} \\
  (|\mathbf{i}| + |\mathbf{b}|).G_{data} + G_{create} & \quad \text{create} \\
\end{cases} \\
c & \equiv & l.p + v
\end{eqnarray}

where $|\mathbf{d}|$, $|\mathbf{i}|$ and $|\mathbf{b}|$ are the sizes, in bytes, of the transaction's associated data, initialisation \& body EVM-code and $G$ is defined in Appendix \ref{app:fees}.

The execution of a valid transaction begins with an irrevocable change made to the state: the nonce of the account of the sender ($s$) is incremented by one and the balance is reduced by the cost, $c$. The gas available for the proceeding computation, $g$, is defined as $l - i$. The proceeding computation, whether contract creation or a message call, results in an eventual state (which may legally be equivalent to the current state), the change to which is deterministic and never invalid: there can be no invalid transactions from this point.

@@

\begin{eqnarray}
\mathbb{S}' & \equiv & \mathbb{S}_C \quad \text{except:} \\
\mathbb{S}'[s]_{balance} & \equiv & \mathbb{S}_C[s]_{balance} + g'.p
\end{eqnarray}

Evaluating $\mathbb{S}_C$ from $\mathbb{S}_R$ depends on the transaction type; either contract-creation or message-call; I will describe and define these separately.

@@

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In in the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:

@@

However, instructions do typically alter one or several components of these values. Altered components, on an listed by instruction are noted in Appendix \ref{app:vm}.

\subsection{Block-tree to Block-chain} \label{ch:ghost}

@@

This scheme notably ignores so-called \textit{stale} blocks: valid, mined blocks, which were propogated too late into the network and thus were beaten to network consensus by a sibling block (one with the same parent). Such blocks become more common as the network propogation time approaches the ideal inter-block time. However, by counting the computation work of stale block headers, we are able to do better: we can utilise this otherwise wasted computation and put it to use in helping to butress the more popular block-chain making it a stronger choice over less popular (though potentially longer) competitors.

@@

As such given a block $B$, $B_td$ is its total difficulty, $B_P$ is its parent block, $B_d$ is its difficulty and $B_\mathbb{U}$ is its set of uncle blocks.

@@

For the release series, we use a more complex proof-of-work. This has yet to be formally defined, but involves two components; firstly that it concerns contract processing, and by extension the evaluation of programs on the EVM. Secondly that it concerns the utilisation of either the block-chain or the full state trie.

@@

\begin{description}
\item[External Actor] A person or other entity able to interface to an Ethereum node, but external to the world of Ethereum. It can interact with Ethereum through depositing signed Transactions and inspecting the block-chain and associated state. Has one (or more) intrinsic Accounts.

@@

\item[Transaction] A piece of data, signed by an External Actor. It represents either a Message or a new Autonomous Object. Transactions are recorded into each block of the block-chain.

@@

\item[Ethereum Browser] (aka Ethereum Reference Client) A cross-platform GUI of an interface similar to a simplified browser (ala Chrome) that is able to host sandboxed applications whose back-end is purely on the Ethereum protocol.

>>>>

\begin{abstract}
The blockchain paradigm when coupled with cryptographically-secured transactions has demonstrated its utility through a number of projects, not least Bitcoin. Each such project can be seen as a simple application on a decentralised, but singleton, compute resource. We can call this paradigm a transactional singleton machine with shared-state.

@@

and $f$ is the Ethereum state transition function. In Ethereum, $f$, together with $S$ are considerably more powerful then any existing comparable system; $f$ allows components to carry out arbitrary computation, while $S$ allows components to store arbitrary state between transactions.

@@

This is the basis of the blockchain paradigm, a model that forms the backbone of Ethereum.

@@

Since the system is decentralised and all parties have an opportunity to create a new block on some older pre-existing block the resultant structure is necessarily a tree of blocks. In order to form a consensus as to which path, from root (the genesis block) to leaf (the block containing the most recent transactions) through this tree structure, known as the blockchain, there must be an agreed-upon scheme. If there is ever a disagreement between nodes as to which root-to-leaf path down the block tree is the `best' blockchain, then a \textit{fork} occurs.

This would mean that past a given point in time (block), multiple states of the system may coexist: some nodes believing one block to contain the canonical transactions, other nodes believing some other block to be canonical, potentially containing radically different or incompatible transactions. This is to be avoided at all costs as the uncertainty that would ensue would likely kill all confidence in the entire system.

@@

The world state (\textit{state}, see Appendix \ref{app:state}), is a mapping between addresses (160-bit identifiers) and account states (a data structure serialised as RLP). Though not stored on the block chain, it is assumed that the implementation will maintain this mapping in a modified Merkle Patricia tree (\textit{trie}, see Appendix \ref{app:trie}). The trie requires a simple database backend that maintains a mapping of bytearrays to bytearrays; we name this underlying database the state database. This has a number of benefits; firstly the root node of this structure is cryptographically dependent on all internal data and as such its hash can be used as a secure identity for the entire system state. Secondly, being an immutable data structure, it allows any previous state (whose root hash is known) to be recalled by simply altering the root hash accordingly. Since we store all such root hashes in the block chain, we are able to trivially revert to old states.

@@

A transaction is a single cryptographically signed instruction sent by an actor external to Ethereum. An external actor can be a person (via a mobile device or desktop computer) or could be from a piece of automated software running on a server. There are two types of transactions: those which result in message calls and those which result in the creation of new contracts. Both types specify a number of common fields:

@@

Both \textbf{body} and \textbf{init} are EVM-code fragments; \textbf{body} is executed each time the contract account receives a message call (either through a transaction or due to the internal execution of code). \textbf{init} is a piece of code that is executed only once at contract creation and that gets discarded immediately thereafter.

@@

This mechanism enforces a homeostasis in terms of the time between blocks; a smaller period between the last two blocks results in an increase in the difficulty level and thus additional computation required, lengthening the likely next period. Conversely, if the period is too large, the difficulty, and expected time to the next block, is reduced.

@@

Where $\mathcal{P}$ is the proof-of-work function (see section \ref{ch:pow}): this evaluates to an pseudo-random number cryptographically dependent on the parameters $H$ and $n$. Given an approximately uniform distribution in the range $[0, 2^{256})$, the expected time to find a solution is proportional to the difficulty, $H_d$.

@@

The other two components in the block are simply a list of the transactions (as defined previously) and a list of uncle block headers (of the same format as above).

@@

Any ether used to purchase gas that is not refunded is delivered to the \textit{coinbase} address, the address of an account typically under the control of the miner. Transactors are free to specify any \textbf{gasPrice} that they wish, however miners are free to ignore transactions as they choose. A higher gas price on a transaction will therefore cost the sender more in terms of Ether and deliver a greater value to the miner and thus will more likely be selected for inclusion by more miners. Miners, in general, will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.

@@

\begin{enumerate}
\item The transaction signature is valid;
\item the transaction nonce is valid (equivalent to the sender account's current nonce);
\item the gas limit is no smaller than the intrinsic gas, $g_0$, used by the transaction;
\item the sender account balance contains at least the cost, $c$, (in wei) required in up-front payment;
\end{enumerate}

Intrinsic gas $g_0$ is calculated as follows:

\begin{eqnarray}
g_0 & \equiv & \begin{cases}
  |\mathbf{d}| G_{data} + G_{call} & \quad \text{call} \\
  (|\mathbf{i}| + |\mathbf{b}|) G_{data} + G_{create} & \quad \text{create} \\
\end{cases}
\end{eqnarray}

where $|\mathbf{d}|$, $|\mathbf{i}|$ and $|\mathbf{b}|$ are the sizes, in bytes, of the transaction's associated data, initialisation and body EVM-code, respectively and $G$ is defined in Appendix \ref{app:fees}.

The up-front cost $c$ is calculated as:

\begin{eqnarray}
c & \equiv & l p + v
\end{eqnarray}

where $l$ is gasLimit, $p$ is gasPrice and $v$ is value as defined parts of the transaction.

The execution of a valid transaction begins with an irrevocable change made to the state: the nonce of the account of the sender ($s$) is incremented by one and the balance is reduced by the cost, $c$. The gas available for the proceeding computation, $g$, is defined as $l - g_0$. The proceeding computation, whether contract creation or a message call, results in an eventual state (which may legally be equivalent to the current state), the change to which is deterministic and never invalid: there can be no invalid transactions from this point.

@@

\begin{eqnarray}
\mathbb{S}' & \equiv & \mathbb{S}_C \quad \text{except:} \\
\mathbb{S}'[s]_{balance} & \equiv & \mathbb{S}_C[s]_{balance} + r p
\end{eqnarray}

Evaluating $\mathbb{S}_C$ from $\mathbb{S}_R$ depends on the transaction type; either contract creation or message call; I will describe and define these separately.

@@

The address of the new contract is defined as being the rightmost 160 bits of the SHA3 hash of RLP encoding of the structure \texttt{[ sender, nonce ]}. In the unlikely event that the address is already in use, it is treated as a big-endian integer and incremented by one until an unused address is arrived at. Thus we define the creation address function $A$:

@@

However, instructions do typically alter one or several components of these values. Altered components listed by instruction are noted in Appendix \ref{app:vm}.

\subsection{Blocktree to Blockchain} \label{ch:ghost}

@@

This scheme notably ignores so-called \textit{stale} blocks: valid, mined blocks, which were propogated too late into the network and thus were beaten to network consensus by a sibling block (one with the same parent). Such blocks become more common as the network propogation time approaches the ideal inter-block time. However, by counting the computation work of stale block headers, we are able to do better: we can utilise this otherwise wasted computation and put it to use in helping to butress the more popular blockchain making it a stronger choice over less popular (though potentially longer) competitors.

@@

As such given a block $B$, $B_{td}$ is its total difficulty, $B_P$ is its parent block, $B_d$ is its difficulty and $B_\mathbb{U}$ is its set of uncle blocks.

@@

For the release series, we use a more complex proof-of-work. This has yet to be formally defined, but involves two components; firstly that it concerns contract processing, and by extension the evaluation of programs on the EVM. Secondly that it concerns the utilisation of either the blockchain or the full state trie.

@@

\begin{description}
\item[External Actor] A person or other entity able to interface to an Ethereum node, but external to the world of Ethereum. It can interact with Ethereum through depositing signed Transactions and inspecting the blockchain and associated state. Has one (or more) intrinsic Accounts.

@@

\item[Transaction] A piece of data, signed by an External Actor. It represents either a Message or a new Autonomous Object. Transactions are recorded into each block of the blockchain.

@@

\item[Ethereum Browser] (aka Ethereum Reference Client) A cross-platform GUI of an interface similar to a simplified browser (ala Chrome) that is able to host sandboxed applications whose backend is purely on the Ethereum protocol.
